On Math

### 2025-05-14 cards/paper.tex
more and more

The \textbf{Euler characteristic} of any polyhedra is denoted by the
Greek letter $\aleph$ (``k-eye'') and is equal to the number:
\begin{equation}
  \aleph = V - E + F
\end{equation}
Any convex polyhedron has
\begin{equation}
  \aleph = 2
\end{equation}
\section{Displacement}
\begin{equation}
  s = ut+\frac{1}{2}gt^2
\end{equation}
where:

@@

\section{Logarithms}
  \begin{tabular}{|l|l|}
    \textbf{Property} & \textbf{Formula} \\
    Product Rule & $\log_a(xy) = \log_a(x) + \log_a(y)$ \\
    Quotient Rule & $\log_a\left(\frac{x}{y}\right) = \log_a(x) - \log_a(y)$ \\
    Power Rule & $\log_a(x^n) = n \cdot \log_a(x)$ \\
    Change of Base & $\log_a(x) = \frac{\log_b(x)}{\log_b(a)}$ \\
    Equating arguments & $\log_af(x) = log_ag(x)$ is the same as $f(x) = g(x)$ \\
  \caption{Fundamental Properties of Logarithms}
  \label{tab:log_properties}

@@

\section{Integrals}
Also called \textit{antiderivatives}. To represent integrals we use an integral
symbol. For example:
\begin{equation}
  \int 2x dx = x^2 + C
\end{equation}
Integrals like this are called 'indefinite integrals' and (in this case)
function being integrated is called an 'integrand'.

>>>>

The \textbf{Euler characteristic} of any polyhedra is denoted by the
Greek letter $\aleph$ (``k-eye'') and is equal to the number:
\begin{equation}
  \aleph = V - E + F
\end{equation}
Any convex polyhedron has
\begin{equation}
  \aleph = 2
\end{equation}
\section{Vectors}
How to call that section?
\section{Displacement}
\begin{equation}
  s = ut+\frac{1}{2}gt^2
\end{equation}
where:

@@

\subsection{Residuals and residual plots}
For dataset of paired numerical observations $(x, y)$ and the corresponding
linear regression model:
  \hat y = f(x)
The \textbf{residual} for a particular observation $(x, y)$ is defined as:
    \text{residual} = \text{actual} - \text{estimated} \\
    y - f(x) = y - \hat y
We subtract the estimated value predicted by model from the actual observed
value:
\begin{itemize}
\item negative residual - model overestimates the true value
\item positive residual - model underestimates the true value
\end{itemize}

Exercises:
\begin{equation}
  \begin{gathered}
    \hat y = 0.02x + 0.8 \\
    \text{for point} P(400, 8.3) \\
    \hat y = 0.02 * 400 + 0.8 = 8.8 \\
    y - \hat y = 8.3 - 8.8 = -0.5
  \end{gathered}
\end{equation}
\section{Logarithms}
\begin{table}[htbp]
  \centering
  \begin{tabular}{|l|l|}
    \hline
    \textbf{Property} & \textbf{Formula} \\
    \hline
    Product Rule & $\log_a(xy) = \log_a(x) + \log_a(y)$ \\
    \hline
    Quotient Rule & $\log_a\left(\frac{x}{y}\right) = \log_a(x) - \log_a(y)$ \\
    \hline
    Power Rule & $\log_a(x^n) = n \cdot \log_a(x)$ \\
    \hline
    Change of Base & $\log_a(x) = \frac{\log_b(x)}{\log_b(a)}$ \\
    \hline
    Equating arguments & $\log_af(x) = log_ag(x)$ is the same as $f(x) = g(x)$ \\
    \hline
  \end{tabular}
  \caption{Fundamental Properties of Logarithms}
  \label{tab:log_properties}
\end{table}

@@

\subsection{Second and higher order derivatives}
The second order derivative is the derivative of a functions first derivative.
It can be written as $f''(x)$. Also
\begin{equation}
  \begin{gathered}
    f''(x) = (f'(x))' \\
    \text{example:} \\
    f(x) = 4x^2 + 3x \\
    f'(x) = 8x+3 \\
    f''(x) = 8
  \end{gathered}
\end{equation}
For Leibnitz notation it can be written as:
\begin{equation}
  \begin{gathered}
    f''(x) = \frac{d^2f}{dx^2} = \frac{d}{dx}(\frac{df}{dx}) \\
    \text{or, for y:} \\
    \frac{d^2y}{dx^2} \\
    \text{for higher order, in general:} \\
    f^{(n)}(x) = \frac{d^n}{dx^n}f(x)
  \end{gathered}
\end{equation}
\section{Integrals}
Also called \textit{antiderivatives}. To represent integrals we use an integral
symbol. For example:
\begin{equation}
  \int 2x dx = x^2 + C
\end{equation}
Integrals like this are called 'indefinite integrals' and (in this case)
function being integrated is called an 'integrand'.
